Manifold Clustering for Latent Structure Block Models

### 2022-03-16 draft/draft.Rmd
minor updates

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\KwData{Adjacency matrix $A$, number of communities $K$, embedding dimensions $p$, $q$, stopping criterion $\epsilon$}
\KwResult{Community assignments $1, ..., K$, curves $g_1, ..., g_K$}
Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.\;
Initialize community labels $z_1, ..., z_n$.\;
\Repeat {$\sum_k \sum_{i \in C_k} \|x_i - g_k(t_i)\|^2 < \epsilon$} {
\For {$k = 1, ..., K$} {
Define $X_k$ as the rows of $X$ for which $z_i = k$.\;
Fit curve $g_k$ and positions $t_{k_i}$ to $X_k$ by minimizing $\sum_{k_i} \|x_{k_i} - g_k(t_{k_i})\|^2$.\;
}
\For {$k = 1, ..., K$} {
Assign $z_i \leftarrow \arg\min_\ell \|x_i - g_\ell(t_i)\|^2$.\
}
}
\caption{$K$-Curves Clustering.}
\end{algorithm}

@@

>>>>

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\KwData{Adjacency matrix $A$, number of communities $K$, embedding dimensions $p$ and $q$.}
\KwResult{Community assignments $1, ..., K$.}
Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.\;
Apply single linkage clustering with $K$ communities on the ASE.\;
\caption{ASE clustering for nonintersecting communities.}
\end{algorithm}

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\KwData{Adjacency matrix $A$, number of communities $K$, embedding dimensions $p$, $q$, stopping criterion $\epsilon$}
\KwResult{Community assignments $1, ..., K$, curves $g_1, ..., g_K$}
Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.\;
Initialize community labels $z_1, ..., z_n$.\;
\Repeat {the change in $\sum_k \sum_{i \in C_k} \|x_i - g_k(t_i)\|^2$ is less than $\epsilon$} {
\For {$k = 1, ..., K$} {
Define $X_k$ as the rows of $X$ for which $z_i = k$.\;
Fit curve $g_k$ and positions $t_{k_i}$ to $X_k$ by minimizing $\sum_{k_i} \|x_{k_i} - g_k(t_{k_i})\|^2$.\;
}
\For {$k = 1, ..., K$} {
Assign $z_i \leftarrow \arg\min_\ell \|x_i - g_\ell(t_i)\|^2$.\
}
}
\caption{$K$-curves clustering.}
\end{algorithm}

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetAlgoLined
\KwData{Adjacency matrix $A$, number of communities $K$, embedding dimensions $p$, $q$, stopping criterion $\epsilon$, $m_k \leq n_k$ known community assignments for each community}
\KwResult{Community assignments $1, ..., K$, curves $g_1, ..., g_K$}
Compute $X$, the ASE of $A$ using the $p$ most positive and $q$ most negative eigenvalues and their corresponding eigenvectors.\;
Fit curves $g_1, ..., g_K$ using each of the $m_1, ..., m_K$ points with known community labels by minimizing $\sum_{j=1}^{m_i} \|x_j - g_k(t_j)\|^2$.\;
Assign labels $z_1, ..., z_n$ to each $x_1, ..., x_n$ by minimizing $\|x_i - g_k(t_i)\|^2$ for $k$, holding the initial known labels constant.\; 
\Repeat {the change in $\sum_k \sum_{i \in C_k} \|x_i - g_k(t_i)\|^2$ is less than $\epsilon$} {
\For {$k = 1, ..., K$} {
Define $X_k$ as the rows of $X$ for which $z_i = k$.\;
Fit curve $g_k$ and positions $t_{k_i}$ to $X_k$ by minimizing $\sum_{k_i} \|x_{k_i} - g_k(t_{k_i})\|^2$.\;
}
\For {$k = 1, ..., K$} {
Assign $z_i \leftarrow \arg\min_\ell \|x_i - g_\ell(t_i)\|^2$, holding the known initial labels constant.\
}
}
\caption{Semi-supervised $K$-curves clustering.}
\end{algorithm}

\begin{theorem}
Let each $g_k$ be smooth. 
Then as $n \to \infty$, the proportion of misclustered vertices approaches $0$ with probability $1$.
\end{theorem}
